Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-16 paper/paper.tex
Revise the related literature section #54

Third, the political science literature on unrecognized states focuses on their consequences on domestic politics.
Economic impacts are relatively understudied.%
\footnote{
	An exception is Witmer and O'Loughlin (2011), who also use nighttime light data to gauge the impact of wars in towns in Georgia and South Ossetia. Our study differs in the coverage of study areas and in the recovery of economic growth from light data. 
} 
Our study complements this strand of the literature to understand the issue of unrecognized states.

>>>>

Third, our study relates to the political science literature on unrecognized states (King 2001, Lunch 2002, Kolsto 2006, O'Loughlin et al.\ 2014, Smolnik 2016, among others). 
In particular, a recent strand of this literature points out that seeking international recognition creates an incentive for politicians in unrecognized states to promote state-building and democratic institutions (Caspersen 2008, 2011; Blakkisrud and Kolsto 2011; Kolsto and Blakkisrud 2012).
Our study complements this literature by uncovering economic consequences of non-recognition which can be interpreted as an indirect impact via state-building and democracy.%
\footnote{
	Witmer and O'Loughlin (2011) use nighttime light data to gauge the impact of wars in towns in Georgia and South Ossetia. Our study differs in the coverage of study areas and in the recovery of economic growth rates from light data. 
}
